Manuscript

### 2015-01-22 inst/simulation/manuscript.Rmd
...

```{r initialize}
library(parallel)
library(doMC)
registerDoMC(cores=detectCores())
library(WTC)
source("~/git/Winter-Track-Counts/setup/WTC-Boot.R")
library(ggplot2)
library(plyr)

@@

    estimates$data <- subset(estimates$data, year == year0)
    if (log) estimates$data$fittedMean <- log(estimates$data$fittedMean)
    density <- estimates$getPopulationDensityInterpolate(getSD=sd, maskPolygon=studyArea$boundary)
    density <- if (sd) density$sd else density$mean
    if (is.null(density) || maxValue(density$rasterStack[[1]]) > 1) stop("Estimation failed.")
    density <- as.data.frame(density$rasterStack[[1]], xy=T)
    density$Scenario <- x$scenario
    density$Iteration <- x$iteration
    density$Model <- modelName
    density$Year <- year0

@@

```{r figure-2-test}
iterations <- as.integer(c(1,1,3,2,5,6))
year <- 2010
densityST <- getEstimatedDensity(scenarios[1], modelNames[1], iterations[1], year=year, sd=FALSE)
p <- ggplot(densityST) + geom_raster(aes_string(x="x", y="y", fill=paste0("X", year))) + scale_fill_gradientn(colours=terrain.colors(100), na.value="transparent") 
saveFigure(p, "tmp_compare_densities_ST.png", width=8)
###

>>>>

```{r initialize}
#library(devtools); install_github("statguy/Winter-Track-Counts")
library(parallel)
library(doMC)
registerDoMC(cores=detectCores())
library(WTC)
source("~/git/Winter-Track-Counts/setup/WTC-Boot.R")
library(ggplot2)
library(plyr)

@@

    estimates$data <- subset(estimates$data, year == year0)
    #if (log) estimates$data$fittedMean <- log(estimates$data$fittedMean)
    density <- estimates$getPopulationDensityInterpolate(getSD=sd, maskPolygon=studyArea$boundary)
    density <- if (sd) density$sd else density$mean
    if (is.null(density) || maxValue(density$rasterStack[[1]]) > 1) stop("Estimation failed.")
    density <- as.data.frame(density$rasterStack[[1]], xy=T)
    density$Scenario <- x$scenario
    density$Iteration <- x$iteration
    density$Model <- modelName
    density$Year <- year0

@@

```{r figure-2-test, eval=FALSE}
x <- data.frame(scenario=scenarios[1], iteration=as.integer(1), stringsAsFactors=F)
modelName <- modelNames[1]
year0 <- year <- 2001
    study <- getStudy(scenario=x$scenario)
    estimates <- study$getModel(modelName=modelName, iteration=x$iteration)
    estimates$modelName <- modelName
    estimates <- study$loadEstimates(estimates)
    estimates$collectEstimates()
    studyArea <- FinlandStudyArea$new(context=context)$setup(tolerance=0.001)
    estimates$data <- subset(estimates$data, year == year0)
    density <- estimates$getPopulationDensityInterpolate(getSD=F, maskPolygon=studyArea$boundary)

iterations <- as.integer(c(1,1,3,2,5,6))
year <- 2010
densityST <- getEstimatedDensity(scenarios[1], modelNames[1], iterations[1], year=year, sd=FALSE)
p <- ggplot(densityST) + geom_raster(aes_string(x="x", y="y", fill=paste0("X", year))) + scale_fill_gradientn(colours=terrain.colors(100), na.value="transparent") 
saveFigure(p, "tmp_compare_densities_ST.png", width=8)
###
